Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-08-26 paper.tex
Started 2nd referee response

\author{Kyle Penner\altaffilmark{1}, Mark Dickinson\altaffilmark{2},
Benjamin Weiner\altaffilmark{3}, Hanae Inami\altaffilmark{2},
Jeyhan Kartaltepe\altaffilmark{2}, Janine Pforr\altaffilmark{4},
Hooshang Nayyeri\altaffilmark{5},
Susan Kassin\altaffilmark{6},
Casey Papovich\altaffilmark{7},
Alexandra Pope\altaffilmark{8}
}

@@

We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
densities per the recommendations in the enhanced imaging products quick start
guide; these sources are excluded.  The remaining 23 galaxies have flux
densities at
0.15 and 0.23$\,\micron$ (NUV and FUV bands), from \emph{GALEX} observations.
H$\alpha$ line
fluxes, from SDSS observations, are from Overzier (private communication).  We
multiply the line fluxes by 1.67 as a fiber-aperture correction
\citep{overzier09}.

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

@@

However, dusty galaxies may disobey the \citet{calzetti00} attenuation
formula, which complicates our interpretation of the more basic relation
between UV and 0.66$\,\micron$ escape fractions---the relation between
escape fractions for just the regions with nonionizing UV-emitting stars
\citep{reddy10,reddy12,reddy15,buat11,buat12,penner12,kriek13}.  The true attenuation
formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
for a given UV escape fraction than does the \citet{calzetti00} formula.  A
formula modified according to
\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
\alephuvha~=
\alephuv$^{0.25}$ instead of \alephuvha~= \alephuv$^{0.33}$.  The combination of
this \citet{kriek13} formula and our result implies that
\alephha~= \alephuvha$^{2.2}$.  The \citep{reddy15} attenuation formula has
\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.4}$.
If the true formula instead has a
much lower 0.66$\,\micron$ escape fraction for a given UV escape
fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
\alephuv$^{0.55}$---we conclude that for dusty
galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
conclusion regarding the uniformity of dust distributions depends on the
assumed attenuation formula.  We cannot reject our hypothesis.  The
\citet{calzetti00} formula does demarcate the upper boundary of \alephha~for the
high-redshift dusty galaxies (bottom left panel of Fig. \ref{fha_fuv}), so
if it is the true formula then at least some dusty galaxies have uniform
dust distributions.  The unambiguous statement we make is that dusty galaxies
have relations between H$\alpha$ and UV escape fractions that are different from
the relation for low-redshift dust-poor galaxies.

@@

@@

\bibitem[Price et al.(2013)]{price13} Price, S.~H., Kriek, M., 
Brammer, G.~B., et al.\ 2014, \apj, 788, 86

>>>>

\author{Kyle Penner\altaffilmark{1}, Mark Dickinson\altaffilmark{2},
Benjamin Weiner\altaffilmark{3}, Hanae Inami\altaffilmark{2},
Jeyhan Kartaltepe\altaffilmark{2}, Janine Pforr\altaffilmark{4},
Hooshang Nayyeri\altaffilmark{5},
Susan Kassin\altaffilmark{6},
Casey Papovich\altaffilmark{7}, and
Alexandra Pope\altaffilmark{8}
}

@@

LBAs are a subset of galaxies from those in \citet{heckman05}.
\citet{heckman05} match galaxies detected in the \emph{GALEX} All-Sky Imaging
Survey to galaxies with spectra from SDSS observations.  The LBA sample contains
galaxies with: (1) luminosity at 0.153$\,\micron, 0.153 \times L_{0.153},
\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}
\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\micron$
and the radius is the half-light radius at 0.35$\,\micron$ ($u$-band);
(3) $z < 0.3$; and (4) no evidence for emission from an AGN.

We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
densities per the recommendations in the enhanced imaging products quick start
guide; these sources are excluded.  The remaining 23 galaxies have flux
densities at
0.15 and 0.23$\,\micron$ (NUV and FUV bands).
H$\alpha$ line
fluxes are from Overzier (private communication).  We
multiply the line fluxes by 1.67 as a fiber-aperture correction
\citep{overzier09}.

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
A low-redshift DOG has either: (1) a flux density at 9$\,\micron$ that is more
than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
A low-redshift control galaxy has a flux density at
12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
Among other criteria the sample of control galaxies is filled such that its
distributions of IR luminosities and stellar masses match those of the sample
of DOGs.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

@@

However, dusty galaxies may disobey the \citet{calzetti00} attenuation
formula, which complicates our interpretation of the more basic relation
between UV and 0.66$\,\micron$ escape fractions---the relation between
escape fractions for just the regions with nonionizing UV-emitting stars
\citep{reddy10,reddy12,reddy15,buat11,buat12,penner12,kriek13}.  The true attenuation
formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
for a given UV escape fraction than does the \citet{calzetti00} formula.  A
formula modified according to
\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
\alephuvha~=
\alephuv$^{0.25}$ instead of \alephuvha~= \alephuv$^{0.33}$.  The combination of
this \citet{kriek13} formula and our result implies that
\alephha~= \alephuvha$^{2.2}$.  The \citet{reddy15} attenuation formula has
\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.4}$.
If the true formula instead has a
much lower 0.66$\,\micron$ escape fraction for a given UV escape
fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
\alephuv$^{0.55}$---we conclude that for dusty
galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
conclusion regarding the uniformity of dust distributions depends on the
assumed attenuation formula.  We cannot reject our hypothesis.  The
\citet{calzetti00} formula does demarcate the upper boundary of \alephha~for the
high-redshift dusty galaxies (bottom left panel of Fig. \ref{fha_fuv}), so
if it is the true formula then at least some dusty galaxies have uniform
dust distributions.  The unambiguous statement we make is that dusty galaxies
have relations between H$\alpha$ and UV escape fractions that are different from
the relation for low-redshift dust-poor galaxies.

@@

\bibitem[Heckman et al.(2005)]{heckman05} Heckman, T.~M., Hoopes, 
C.~G., Seibert, M., et al.\ 2005, \apjl, 619, L35

@@

\bibitem[Price et al.(2014)]{price13} Price, S.~H., Kriek, M., 
Brammer, G.~B., et al.\ 2014, \apj, 788, 86
